Effects of Antenna Beam Chromaticity on Redshifted 21~cm Power Spectrum and Implications for Hydrogen Epoch of Reionization Array

### 2016-03-23 ForegroundSimulations/ms.tex
Minor changes throughout
From ffe0557 (fgsim):
====================

In ms.tex,

(*) Minor changes throughout

\citet{deb16} describe the HERA instrument in detail. Here, we provide a brief summary of the telescope currently under construction on the South African SKA site.

@@

320 core elements of HERA will be arranged in a compact hexagonal grid, split into three displaced segments to cover the $uv$-plane with sub-element sampling density. The core will be supplemented by 30 additional outrigger elements to tile the $uv$-plane with instantaneously complete sub-aperture sampling out to $250\lambda$ and complete aperture-scale sampling out to $350\lambda$ (at 150~MHz). The layout and its advantages are discussed in \citet{dil16}.

@@

A brief description of the delay spectrum technique \citep{par12a,par12b} is provided here. We borrow the notation used in \citet{thy15a}.

{\it Visibilities} measured by an interferometer are given by \citep{van34,zer38,tho01}:
\begin{align}\label{eqn:obsvis}
  V_b(f) &= \iint\limits_\textrm{sky} A(\hat{\boldsymbol{s}},f)\,I(\hat{\boldsymbol{s}},f)\,e^{-i2\pi f\frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}}\,\dif\Omega,
\end{align}
where, $\boldsymbol{b}$ is the vector joining antenna pairs (commonly referred to as the baseline vector), $\hat{\boldsymbol{s}}$ is the unit vector denoting direction on the sky, $f$ denotes frequency, $c$ is the speed of light, $\dif\Omega$ is the solid angle element to which $\hat{\boldsymbol{s}}$ is the unit normal vector, $I(\hat{\boldsymbol{s}},f)$ and $A(\hat{\boldsymbol{s}},f)$ are the sky brightness and antenna's directional power pattern, respectively, as a function of $\hat{\boldsymbol{s}}$ and $f$. The {\it delay spectrum}, $\tilde{V}_b(\tau)$, is defined as the inverse Fourier transform of $V_b(f)$ along the frequency coordinate:
\begin{align}\label{eqn:delay-transform}
  \tilde{V}_b(\tau) &\equiv \int V_b(f)\,W(f)\,e^{i2\pi f\tau}\,\dif f,
\end{align}
where, $W(f)$ is a spectral weighting function which can be chosen to control the quality of the delay spectrum \citep{ved12,thy13}, and $\tau$ represents the signal delay between antenna pairs:
\begin{equation}\label{eqn:delay}
  \tau = \frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}.
\end{equation}

The delay spectrum has a close resemblance to cosmological H~{\sc i} spatial power spectrum and is defined as:
\begin{align}\label{eqn:delay-power-spectrum}
  P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel) &\equiv |\tilde{V}_b(\tau)|^2\left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
\end{align}
with
\begin{align}
  \boldsymbol{k}_\perp &\equiv \frac{2\pi(\frac{\boldsymbol{b}}{\lambda})}{D}, \label{eqn:kperp-baseline}\\
  k_\parallel &\equiv \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, \label{eqn:kprll-delay}
\end{align}
where, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $\boldsymbol{k}_\perp$ and $k_\parallel$ are the transverse (on the sky) and line-of-sight (into the sky) wavenumbers respectively, $f_{21}$ is the rest-frame frequency of the 21~cm spin-flip transition of H~{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight corresponding to $\Delta B$, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology. Following \citet{par14},
\begin{align}
  \Omega\Delta B &= \iint \left|A(\hat{\boldsymbol{s}},f)\,W(f)\right|^2\,\dif\Omega\,\dif f,
\end{align}
which is related to the cosmic volume probed by the instrument. In this paper, we use $\Omega_\textrm{M}=0.27$, $\Omega_\Lambda=0.73$, $\Omega_\textrm{K}=1-\Omega_\textrm{M}-\Omega_\Lambda$, $H_0=100\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.

We note that these visibilities and delay power spectra are dependent on right ascension (RA) of the pointing as well as the frequency band. However, we defer expressing them explicitly as a function of pointing and center frequency (or redshift) to later sections where it becomes necessary.

@@

In this paper, we investigate the spectral properties of the proposed dish design through their effects on the resultant foreground delay power spectrum and the constraints they place on attenuation required to suppress reflections in the instrument.

@@

In a related series of papers, \citet{neb16} discuss the agreement of these simulated antenna beam patterns with actual measurements, \citet{ewa16} model the reflections and return loss expected in the proposed antenna-feed assembly, and \citet{pat16} present measurements quantifying the reflections. Our focus in this paper is to investigate chromaticity of antenna power patterns from the point of view of their impact on foreground contamination in delay power spectra.

@@

Since our aim in this paper is to quantify EoR-foreground power ratio without employing any sophisticated {\it foreground removal} techniques, we turn our attention to {\it foreground avoidance} strategy that employs spectral weighting technique. In such a scheme, specific choices for spectral weighting function, $W(f)$, have been found to be effective in reducing foreground contamination by many orders of magnitude \citep{thy13} and is regularly used in EoR data analysis \citep{par12a}. For instance, a {\it Blackman-Harris} function \citep{har78} has a dynamic range of $\sim$100 -- 120~dB in delay power spectrum and a reduced effective bandwidth, with:
\begin{align}\label{eqn:Beff}
  \epsilon &= \frac{1}{B} \int_{-B/2}^{+B/2} |W(f)|^2\,\dif f, \\
  \textrm{and,}\quad B_\textrm{eff} &= \epsilon\,B,
  % B_\textrm{eff} &= \int_{-B/2}^{+B/2} |W(f)|^2\,\dif f.
\end{align}
where, $1-\epsilon$ is the loss in overall spectral sensitivity and $B_\textrm{eff}$ is the effective bandwidth. For a {\it Blackman-Harris} window function denoted by $W_\textrm{BH}(f)$, $\epsilon \approx 50\%$. % Hence, the window spans a total of $2N$ frequency channels each of width $\Delta f$ to have $B_\textrm{eff} \approx N\,\Delta f$.

Considering that the dynamic range required to suppress foreground contamination in the {\it EoR window} may probably be even higher than that provided by a {\it Blackman-Harris} window function, we use a modified version given by the convolution of a {\it Blackman-Harris} window with itself:
\begin{align}\label{eqn:bhw2}
  W(f) &= W_\textrm{BH}(f) \ast W_\textrm{BH}(f).
\end{align}

@@

This is an enormous gain in sidelobe characteristics for a small loss of sensitivity relative to a simple {\it Blackman-Harris} weighting. This will ensure that the contamination resulting from spillover of foregrounds along the line-of-sight $k$-modes are limited only by intrinsic spectral structures in the foregrounds or beam patterns and not by sidelobes from spectral weighting. In this paper, we apply this modified spectral weighting function defined in equation~\ref{eqn:bhw2} whenever foregrounds are represented in the Fourier delay domain.

In HERA-19 array layout, there are 30 unique baseline vectors and 8 unique baseline lengths. Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern at arbitrary pointings on the sky. In all these panels, the full-band foreground delay power spectra obtained with achromatic, {\it Airy} and fully chromatic simulated beam patterns are shown in black, red, and blue respectively. The brightening of foreground power near the horizon limits (vertical dotted lines) due to the {\it pitchfork} effect \citep{thy15a,thy15b} is prominently seen in all cases. A clear broadening of spillover-wings outside the horizon limits is seen with increasing chromaticity as the beam is changed from the achromatic to the {\it Airy} to the chromatic simulated model. For instance, the spillover from foreground delay power spectrum obtained with chromatic beam pattern is restricted to $|k_\parallel| \lesssim 0.2\,h$~Mpc$^{-1}$, with the {\it Airy} pattern it is restricted to $|k_\parallel| \lesssim 0.15\,h$~Mpc$^{-1}$, while with the achromatic beam it is restricted to $|k_\parallel| \lesssim 0.12\,h$~Mpc$^{-1}$ even on longest baseline lengths. It is also noted that despite the extreme dynamic range of the spectral weighting function employed, the tail of the foreground spillover at $|k_\parallel| \gtrsim 0.2\,h$~Mpc$^{-1}$ with an {\it Airy} beam pattern is many orders of magnitude higher than that using an achromatic beam while that from the simulated chromatic beam is even higher than from an {\it Airy} pattern by a few orders of magnitude. This signals that the foreground spillover shown are truly limited by intrinsic spectral features in the antenna beam patterns.

@@

This clearly demonstrates that higher the beam chromaticity, the farther the foreground contamination inherently extends along $k_\parallel$. Thus, the chromaticity of antenna beam needs to be carefully controlled in EoR experiments in order to keep the foreground systematics sufficiently low.

Such a significant spillover is not bound by the horizon limits of the {\it foreground wedge} because this is caused by spectral structure in the antenna beam pattern which is independent of the position-dependent geometric delays. As a result delay-based complex deconvolution techniques such as CLEAN \citep{tay99,par09,par12b} that rely on smoothness of foreground spectra and only spectral window shape will not have adequate information to accurately deconvolve intrinsic supra-horizon spillover arising from the chromaticity of the antenna beam. While delay power spectrum estimation using {\it foreground removal} strategy that accounts for direction- and beam chromaticity-dependent effects is possible, we leave it for future work.

@@

One of the primary causes for spectral structure in antenna power patterns is reflections in the instrument. \citet{pat16} and \citet{ewa16} discuss the measured and simulated reflections respectively between a dish and its feed. Reflection between structures and signal paths from different antennas also causes chromaticity in the antenna beam. In this section, we provide cosmologically motivated design specifications on instrument systematics caused by these two types of reflections.

The effect of reflections it to shift the measured foreground power to higher modes in $\tau$ (or in $k_\parallel$) and thus cause further contamination in these higher $k_\parallel$-modes which are considered sensitive for EoR H{\sc i} signal detection. These delay shifts introduce ripples in the spectrum. The net chromaticity in the measurements is the product of spectral structure arising out of the intrinsic nature of foreground emission, the baseline- and position-dependent frequency structure of the geometric phases, the spectral features in the antenna power pattern besides any other spectral structures in the instrument unaccounted for. In the Fourier domain these factors have a convolving effect. In order to isolate the requirements on beam chromaticity from other sources of chromaticity, we start with an antenna beam in which those spectral structures are absent but the intrinsic chromaticity of foregrounds and the geometric phases of baselines are included.

We define the required attenuation on the reflected foreground power as the ratio: 
\begin{align}\label{eqn:attenuation}
  \Gamma_{k_\textrm{p}}(\tau) \geq \max_{|k_\parallel|>k_\textrm{p}}\left\{\frac{P_\textrm{FG}(k_\parallel - \frac{\dif k_\parallel}{\dif \tau}\,\tau)}{P_\textrm{H{\sc i}}(k_\parallel)}\right\}^{1/2},
\end{align}
where, $P_\textrm{H{\sc i}}(k_\parallel)$ is the EoR H{\sc i} power spectrum for the chosen antenna spacing, $P_\textrm{FG}(k_\parallel)$ is the foreground delay power spectrum obtained with the spectral weighting function applied over the full-band of the three uniquely oriented 14.6~m antenna spacings further averaged over a 0--12 hr local sidereal time (LST) range and over both positive and negative $k_\parallel$-modes, $\tau$ is the delay caused by reflections, and $\dif k_\parallel/\dif \tau$ is the {\it jacobian} in the transformation of $\tau$ to $k_\parallel$ (see equation~\ref{eqn:kprll-delay}). Thus, $\Gamma_{k_\textrm{p}}(\tau)$ is determined by the requirement that the reflected foreground power obtained by shifting in delay is below the EoR H{\sc i} signal power in line-of-sight spatial scales of interest given by $|k_\parallel|>k_\textrm{p}$.

Both EoR models were used separately in this analysis to reduce the dependence of design specifications for reflections on any single model. However, we found similar results except for minor differences caused by small amplitude differences between the two EoR models. Hence, we only use results from using EoR model 1 at 150~MHz ($z\approx 8.47$).

@@

For reflections caused by dish-feed assembly, we use $P_\textrm{FG}(k_\parallel)$ obtained with the achromatic beam model on a 14.6~m baseline in equation~\ref{eqn:attenuation}. Fig.~\ref{fig:fg-reflections-achrmbeam} shows $\Gamma_{k_\textrm{p}}(\tau)$ (in dB) for $k_\textrm{p}$ chosen to be 0.1~$h$~Mpc$^{-1}$ (solid), 0.15~$h$~Mpc$^{-1}$ (dashed), and 0.2~$h$~Mpc$^{-1}$ (dotted). These curves set an upper limit for the reflected foreground power to lie below the EoR H{\sc i} signal power as a function of delays. These reflections are primarily caused in the dish-feed assembly and to some extent in other subsystems not accounted for. It implies that if these reflections are attenuated to levels that lie in the regions below the different shaded regions, such spectral systematics in the instrument will not hinder detection of EoR in those corresponding $k_\parallel$-modes of interest.

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{spec_on_achrmbeam_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
\caption{Minimum required attenuation (in dB) for internal dish-feed reflections required to keep the reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (solid), $0.15\,h$~Mpc$^{-1}$ (dashed) and $0.2\,h$~Mpc$^{-1}$ (dotted). This is obtained on 14.6~m antenna spacing for EoR model 1 at 150~MHz ($z\approx 8.47$) and foreground power obtained with an achromatic antenna beam model. When the attenuation on dish-feed reflections is higher than these limits (outside the shaded regions), EoR will be detectable in respective $k_\parallel$-modes despite these reflections.}
\label{fig:fg-reflections-achrmbeam}
\end{figure}

The elbow-shaped turnover is a measure of the most severe requirement on attenuation of reflections. This depends sensitively on the chosen $k_\parallel$ modes. For instance, the attenuation required is $\gtrsim 54$~dB at $\sim 200$~ns for $k_\textrm{p}=0.1\,h$~Mpc$^{-1}$, $\gtrsim 56$~dB at $\sim 300$~ns for $k_\textrm{p}=0.15\,h$~Mpc$^{-1}$ and $\gtrsim 58$~dB at $\sim 400$~ns for $k_\textrm{p}=0.2\,h$~Mpc$^{-1}$. Measurements by \citet{pat16} show that the return losses for HERA lie well within the regions excluded by the shaded regions thus implying that the attenuation is well above the lower limit and hence will not prevent EoR detection.

@@

In both types of reflections discussed, similar design limits on reflections on various antenna spacings were also studied. With increase in baseline length, the amplitude of foreground power decreases but the {\it foreground window} also widens. This means the amplitude of reflections required to be suppressed is lower but there is lesser room along delay axis before the reflected foreground modes shift to and contaminate the $k_\parallel$-modes of interest. As a result, the elbow-shaped design constraints shift upward and leftward. For instance, in the presence of dish-feed reflections, it will still be feasible to probe $k_\parallel > 0.15\,h$~Mpc$^{-1}$ with the 58.4~m baselines but not other larger scales.

@@

Here our goal is to estimate the EoR-foreground dynamic range (ratio of EoR signal power to foreground power) in the presence of antenna beam chromaticity, using HERA as an example. % As stated earlier, we estimate this ratio for HERA in the most conservative scenario where we consider only {\it foreground avoidance} under simple spectral weighting scheme. We emphasize that other strategies involving {\it foreground removal} and inverse covariance-based weighting schemes will produce more optimal results than presented here. 
In order to avoid signal evolution across the entire bandwidth, we use subbands in which EoR signal evolution is not expected to be significant. These subbands with $B_\textrm{eff}=10$~MHz are defined by spectral weights obtained by convolution of {\it Blackman-Harris} window with itself. These subbands are centered at 150~MHz and 170~MHz to estimate EoR-foreground dynamic range at $z \approx 8.47$ and $z \approx 7.36$ respectively. We use both EoR models 1 and 2 to reduce the dependence of this analysis on any single EoR model.

@@

We estimate the ratio of EoR signal and foreground powers for HERA, where the latter is obtained with three antenna beams of different chromaticities. Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} and \ref{fig:asm-dps-beam-chromaticity-baselines-170-subband} show the EoR signal and foreground power in 150~MHz and 170~MHz subbands respectively. EoR models 1 and 2 are shown in cyan and gray respectively. The foreground delay power spectra obtained with achromatic, {\it Airy} and simulated chromatic antenna patterns are shown in black, red, and blue respectively. Each panel corresponds to a unique baseline vector, same as in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}.

@@

For the baselines considered, $\rho(\boldsymbol{b},f_0,\alpha)$ increases with longer baselines. We attribute this to the much steeper dependence of foreground emission on baseline length than that of EoR H{\sc i} power. This is also confirmed from Fig.~\ref{fig:subbands} where the peak and sidelobe levels of foreground power obtained with the simulated chromatic antenna beam on the 14.6~m baseline, which is sensitive to diffuse emission, progressively drops by two orders of magnitude on the 58.4~m baseline where diffuse emission is not as dominant. Hence, from a foreground contamination standpoint, the shortest baselines are less sensitive than the longer ones in the HERA-19 layout.

>>>>

\citet{deb16} describe the HERA instrument in detail. We provide a summary of the instrument currently under construction on the South African SKA site.

@@

320 core elements of HERA will be arranged in a compact hexagonal grid, split into three displaced segments to cover the $uv$-plane with sub-element sampling density. The core will be supplemented by 30 additional outrigger elements to tile the $uv$-plane with instantaneously complete sub-aperture sampling out to $250\lambda$ and complete aperture-scale sampling out to $350\lambda$ (at 150~MHz). The layout is discussed in \citet{dil16}.

@@

The delay spectrum technique \citep{par12a,par12b} is briefly described here. We borrow the notation used in \citet{thy15a}.

{\it Visibilities} measured by an interferometer are given by \citep{van34,zer38,tho01}:
\begin{align}\label{eqn:obsvis}
  V_b(f) &= \int\limits_\textrm{sky} A(\hat{\boldsymbol{s}},f)\,I(\hat{\boldsymbol{s}},f)\,e^{-i2\pi f\frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}}\,\dif\Omega,
\end{align}
where, $\boldsymbol{b}$ is the vector joining antenna pairs (commonly referred to as the baseline vector), $\hat{\boldsymbol{s}}$ is the unit vector denoting direction on the sky, $f$ denotes frequency, $c$ is the speed of light, $\dif\Omega$ is the solid angle element to which $\hat{\boldsymbol{s}}$ is the unit normal vector, $I(\hat{\boldsymbol{s}},f)$ and $A(\hat{\boldsymbol{s}},f)$ are the sky brightness and antenna's directional power pattern, respectively, as a function of $\hat{\boldsymbol{s}}$ and $f$. The {\it delay spectrum}, $\tilde{V}_b(\tau)$, is defined as the inverse Fourier transform of $V_b(f)$ along the frequency coordinate:
\begin{align}\label{eqn:delay-transform}
  \tilde{V}_b(\tau) &\equiv \int V_b(f)\,W(f)\,e^{i2\pi f\tau}\,\dif f,
\end{align}
where, $W(f)$ is a spectral weighting function which can be chosen to control the quality of the delay spectrum \citep{ved12,thy13}, and $\tau$ represents the signal delay between antenna pairs:
\begin{equation}\label{eqn:delay}
  \tau = \frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}.
\end{equation}

The delay spectrum has a close resemblance to cosmological H{\sc i} spatial power spectrum and is defined as:
\begin{align}\label{eqn:delay-power-spectrum}
  P(\boldsymbol{b},k_\parallel) &\equiv |\tilde{V}_b(\tau)|^2\left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
\end{align}
with
\begin{align}
  \boldsymbol{k}_\perp &\equiv \frac{2\pi(\frac{\boldsymbol{b}}{\lambda})}{D}, \label{eqn:kperp-baseline}\\
  k_\parallel &\equiv \frac{2\pi\,f_{21}H_0\,E(z)}{c(1+z)^2}\,\tau, \label{eqn:kprll-delay}
\end{align}
where, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $\boldsymbol{k}_\perp$ and $k_\parallel$ are the transverse (on the sky) and line-of-sight (into the sky) wavenumbers respectively, $f_{21}$ is the rest-frame frequency of the 21~cm spin-flip transition of H{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight corresponding to $\Delta B$, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology. $P(\boldsymbol{b},k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$. In this paper, we use $\Omega_\textrm{M}=0.27$, $\Omega_\Lambda=0.73$, $\Omega_\textrm{K}=1-\Omega_\textrm{M}-\Omega_\Lambda$, $H_0=100\,$km$\,$s$^{-1}\,$Mpc$^{-1}$. 
\begin{align}
  \Omega\Delta B &= \iint \left|A(\hat{\boldsymbol{s}},f)\,W(f)\right|^2\,\dif\Omega\,\dif f,
\end{align}
is related to the cosmic volume probed by the instrument \citet{par14}.

We note that these visibilities and delay power spectra are dependent on right ascension (RA) of the pointing as well as the frequency band. However, we defer expressing them explicitly as a function of pointing and frequency band (or redshift) to later sections where necessary.

@@

In this paper, we investigate the spectral properties of the proposed dish design from a foreground contamination standpoint and the constraints they place on attenuation required to suppress reflections in the instrument.

@@

In a related series of papers, \citet{neb16} discuss the agreement of these simulated antenna beam patterns with actual measurements, \citet{ewa16} model the reflections and return loss expected in the proposed antenna-feed assembly, and \citet{pat16} present measurements quantifying the reflections. Our focus in this paper is to investigate chromaticity of antenna power patterns from the point of view of their impact on foreground contamination.

@@

Since our aim in this paper is to quantify EoR-foreground power ratio without employing any sophisticated {\it foreground removal} techniques, we turn our attention to {\it foreground avoidance} strategy that employs spectral weighting technique. Specific choices for spectral weighting function, $W(f)$, have been found to be effective in reducing foreground contamination by many orders of magnitude \citep{thy13} and is regularly used in EoR data analysis \citep{par12a}. For instance, a {\it Blackman-Harris} function \citep{har78} has a dynamic range of $\sim$100 -- 120~dB in delay power spectrum and a reduced effective bandwidth, with:
\begin{align}\label{eqn:Beff}
  \epsilon &= \frac{1}{B} \int_{-B/2}^{+B/2} |W(f)|^2\,\dif f, \\
  \textrm{and,}\quad B_\textrm{eff} &= \epsilon\,B,
  % B_\textrm{eff} &= \int_{-B/2}^{+B/2} |W(f)|^2\,\dif f.
\end{align}
where, $B$ denotes the end-to-end range of the observing band, $1-\epsilon$ is the loss in overall spectral sensitivity and $B_\textrm{eff}$ is the effective bandwidth. For a {\it Blackman-Harris} window function denoted by $W_\textrm{BH}(f)$, $\epsilon \approx 50\%$. % Hence, the window spans a total of $2N$ frequency channels each of width $\Delta f$ to have $B_\textrm{eff} \approx N\,\Delta f$.

As the dynamic range required to suppress foreground contamination in the {\it EoR window} may probably be even higher than that provided by a {\it Blackman-Harris} window function, we use a modified version given by convolving a {\it Blackman-Harris} window with itself:
\begin{align}\label{eqn:bhw2}
  W(f) &= W_\textrm{BH}(f) \ast W_\textrm{BH}(f).
\end{align}

@@

This is an enormous gain in sidelobe characteristics for a small loss of sensitivity relative to a {\it Blackman-Harris} weighting. This will ensure that the contamination resulting from spillover of foregrounds along the line-of-sight $k$-modes are limited only by intrinsic spectral structures in the foregrounds or beam patterns and not by sidelobes from spectral weighting. In this paper, we apply this modified spectral weighting function defined in equation~\ref{eqn:bhw2} whenever foregrounds are represented in the Fourier delay domain.

In HERA-19 array layout, there are 30 unique baseline vectors and 8 unique baseline lengths. Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern at arbitrary pointings on the sky. In all these panels, the full-band foreground delay power spectra obtained with achromatic, {\it Airy} and chromatic simulated beam patterns are shown in black, red, and blue respectively. The brightening of foreground power near the horizon limits (vertical dotted lines) due to the {\it pitchfork} effect \citep{thy15a,thy15b} is prominently seen in all cases. A clear broadening of spillover-wings outside the horizon limits is seen with increasing chromaticity as the beam is changed from the achromatic to the {\it Airy} to the chromatic simulated model. For instance, the spillover from foreground delay power spectrum obtained with chromatic beam pattern is restricted to $|k_\parallel| \lesssim 0.2\,h$~Mpc$^{-1}$, with the {\it Airy} pattern it is restricted to $|k_\parallel| \lesssim 0.15\,h$~Mpc$^{-1}$, while with the achromatic beam it is restricted to $|k_\parallel| \lesssim 0.12\,h$~Mpc$^{-1}$ even on longest baseline lengths. It is also noted that despite the extreme dynamic range of the spectral weighting function employed, the tail of the foreground spillover at $|k_\parallel| \gtrsim 0.2\,h$~Mpc$^{-1}$ with an {\it Airy} beam pattern is many orders of magnitude higher than that using an achromatic beam while that from the simulated chromatic beam is even higher than from an {\it Airy} pattern by a few orders of magnitude. Thus, the foreground spillover shown is truly limited by intrinsic spectral features in the antenna beam patterns.

@@

This clearly demonstrates that higher the beam chromaticity, the farther the foreground contamination inherently extends along $k_\parallel$. Thus, the chromaticity of antenna beam needs to be controlled in EoR experiments to keep the foreground systematics sufficiently low.

Such a significant spillover is not bound by the horizon limits as this is caused by spectral structure in the antenna beam pattern and is independent of geometric phases. Hence, delay-based complex deconvolution techniques \citep{par09,par12b} that rely on smoothness of foreground spectra and only spectral window shape will not have adequate information to accurately deconvolve intrinsic supra-horizon spillover arising from the chromaticity of the antenna beam. While delay power spectrum estimation using {\it foreground removal} strategy that accounts for direction- and beam chromaticity-dependent effects is possible, we leave it for future work.

@@

A primary cause for spectral structure in antenna power patterns is reflections in the instrument. \citet{pat16} and \citet{ewa16} discuss the measured and simulated reflections respectively between a dish and its feed for HERA. Reflections between different antennas also causes chromaticity in the antenna beam. In this section, we provide cosmologically motivated design specifications on instrument systematics caused by these two types of reflections.

Reflections shift the measured foreground power to higher modes in $\tau$ (or in $k_\parallel$) and thus cause further contamination in these critical higher $k_\parallel$-modes. These delay shifts introduce ripples in the spectrum. The net chromaticity in the measurements is the product of spectral structure arising out of the intrinsic nature of foreground emission, the baseline- and position-dependent frequency structure of the geometric phases, the spectral features in the antenna power pattern besides any other spectral structures in the instrument unaccounted for. In the Fourier domain these factors have a convolving effect. In order to isolate the requirements on beam chromaticity from other sources of chromaticity, we start with an antenna beam in which those spectral structures are absent but the intrinsic chromaticity of foregrounds and the geometric phases of baselines are included.

We define the required attenuation on the reflected foreground power as the ratio: 
\begin{align}\label{eqn:attenuation}
  \Gamma_{k_\textrm{p}}(\boldsymbol{b},\tau) \geq \max_{|k_\parallel|>k_\textrm{p}}\left\{\frac{\left\langle P_\textrm{FG}(\boldsymbol{b},k_\parallel - \frac{\dif k_\parallel}{\dif \tau}\,\tau)\right\rangle}{P_\textrm{H{\sc i}}(|\boldsymbol{b}|,k_\parallel)}\right\}^{1/2},
\end{align}
where, $\tau$ is the delay caused by reflections, and $\dif k_\parallel/\dif \tau$ is the {\it jacobian} in the transformation of $\tau$ to $k_\parallel$ (see equation~\ref{eqn:kprll-delay}). $P_\textrm{H{\sc i}}(|\boldsymbol{b}|,k_\parallel)$ is the EoR H{\sc i} delay power spectrum. $P_\textrm{FG}(\boldsymbol{b},k_\parallel)$ is the full-band foreground delay power spectrum. The angular brackets denote averaging over baseline vectors of the specified length, and a local sidereal time (LST) range. Thus, $\Gamma_{k_\textrm{p}}(\tau)$ is determined by the requirement that the reflected foreground power obtained by shifting in delay lies below the EoR H{\sc i} signal power in line-of-sight spatial scales of interest, $|k_\parallel|>k_\textrm{p}$.

Both EoR models were employed in this analysis to reduce the dependence of design specifications on any single model. However, we found similar results except for minor differences caused by small amplitude differences between the two EoR models. Hence, we only present results from using EoR model 1 at 150~MHz.

@@

For reflections caused by dish-feed assembly, we use $P_\textrm{FG}(k_\parallel)$ obtained with the achromatic beam model on 14.6~m baselines in a 0--12 hr LST range. Fig.~\ref{fig:fg-reflections-achrmbeam} shows $\Gamma_{k_\textrm{p}}(\tau)$ (in dB) for $k_\textrm{p}$ chosen to be 0.1~$h$~Mpc$^{-1}$ (solid), 0.15~$h$~Mpc$^{-1}$ (dashed), and 0.2~$h$~Mpc$^{-1}$ (dotted). These curves set an upper limit for the reflected foreground power to lie below the EoR H{\sc i} signal power as a function of delays. These reflections are primarily caused in the dish-feed assembly and to some extent in other subsystems not accounted for. It implies that if attenuated to levels that lie in the regions below the different shaded regions, such spectral systematics in the instrument will not hinder detection of EoR in those corresponding $k_\parallel$-modes of interest.

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{spec_on_achrmbeam_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
\caption{Minimum required attenuation (in dB) for internal dish-feed reflections required to keep the reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (solid), $0.15\,h$~Mpc$^{-1}$ (dashed) and $0.2\,h$~Mpc$^{-1}$ (dotted). This is obtained on 14.6~m antenna spacing for EoR model 1 at 150~MHz ($z\approx 8.47$) and foreground power obtained with an achromatic antenna beam model. For EoR to be detectable in respective $k_\parallel$-modes despite these systematics, the attenuation of reflections must exceed these limits (outside the shaded regions).}
\label{fig:fg-reflections-achrmbeam}
\end{figure}

The elbow-shaped turnover is a measure of the most severe requirement on attenuation of reflections. This depends sensitively on the choice of $k_p$. For instance, the attenuation required is $\gtrsim 54$~dB at $\sim 200$~ns for $k_\textrm{p}=0.1\,h$~Mpc$^{-1}$, $\gtrsim 56$~dB at $\sim 300$~ns for $k_\textrm{p}=0.15\,h$~Mpc$^{-1}$ and $\gtrsim 58$~dB at $\sim 400$~ns for $k_\textrm{p}=0.2\,h$~Mpc$^{-1}$. Measurements are underway \citep{pat16} to confirm that the return losses in the HERA design lie well within the regions excluded by the shaded regions.

@@

Similar design limits on reflections on various antenna spacings were also studied. With increase in baseline length, the amplitude of foreground power decreases but the {\it foreground window} also widens. This means the amplitude of reflections required to be suppressed is lower but there is lesser room along delay axis before the reflected foreground modes shift to and contaminate the $k_\parallel$-modes of interest. As a result, the elbow-shaped design constraints shift upward and leftward. For instance, in the presence of dish-feed reflections, it will still be feasible to probe $k_\parallel > 0.15\,h$~Mpc$^{-1}$ with the 58.4~m baselines but not other larger scales.

@@

We estimate the EoR-foreground dynamic range (ratio of EoR signal and foreground powers) for both EoR models in the presence of antenna beam chromaticity, using HERA as an example. % As stated earlier, we estimate this ratio for HERA in the most conservative scenario where we consider only {\it foreground avoidance} under simple spectral weighting scheme. We emphasize that other strategies involving {\it foreground removal} and inverse covariance-based weighting schemes will produce more optimal results than presented here. 
In order to avoid signal evolution across the entire band, we use subbands in which EoR signal evolution is not expected to be significant. These subbands with $B_\textrm{eff}=10$~MHz are defined by spectral weights in equation~\ref{eqn:bhw2}. These subbands are centered at 150~MHz and 170~MHz to estimate EoR-foreground dynamic range at $z \approx 8.47$ and $z \approx 7.36$ respectively.

@@

We estimate EoR-foreground dynamic range for HERA using antenna beams of different chromaticities. Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} and \ref{fig:asm-dps-beam-chromaticity-baselines-170-subband} show the EoR signal and foreground power in 150~MHz and 170~MHz subbands respectively. EoR models 1 and 2 are shown in cyan and gray respectively. The foreground delay power spectra obtained with achromatic, {\it Airy} and simulated chromatic antenna patterns are shown in black, red, and blue respectively. Each panel corresponds to a baseline vector, same as in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}.

@@

For the baselines considered, $\rho(\boldsymbol{b},f_0,\alpha)$ increases with baseline length. We attribute this to the much steeper dependence of foreground emission (predominantly diffuse emission) on baseline length than that of EoR H{\sc i} power. This is also confirmed from Fig.~\ref{fig:subbands} where the peak and sidelobe levels of foreground power obtained with the simulated chromatic antenna beam on the 14.6~m baseline, progressively drops by two orders of magnitude on the 58.4~m baseline. Hence, from a foreground contamination standpoint, the shortest baselines are less sensitive than longer ones in HERA-19 layout.
